AFQ-Insight

### 2019-12-16 reports/manuscript/sections/introduction.tex
Update reports/manuscript/sections/introduction.tex

Leveraging this fact, one of the most powerful methods currently
available to put macro- and micro-structure together is
\emph{tractometry}: assessment of the physical properties of the white
matter along specific tracts \cite{Bells2011-cf}. Though there are
several different available implementations of this overall idea,
the principles are similar \cite{yeatman2012tract, Yendiki2011-ay,
Wassermann2016-iv, ODonnell2009-uu}: tractometry begins by delineating
the parts of the white matter that belong to different major ``tracts''
(i.e. anatomical or functional groups of white matter fibers),
such as the corticospinal tract or arcuate fasciculus, assigning
tractography generated streamlines to ``bundles,'' which approximate
the anatomical tracts, and sampling biophysical properties (such as
fractional anisotropy or mean diffusivity) along the length of these
bundles. Whereas the identification of the anatomical correlates
of tractography-generated streamlines is an open problem, the
correspondence between tractometry's bundles and anatomical tracts is
well supported \cite{Catani2002-vu}. Tract-based diffusion metrics are
therefore appropriate degrees of freedom with which to understand the
white-matter correlates of cognitive function or disease.

>>>>

Leveraging this fact, one of the most powerful methods currently
available to put macro- and micro-structure together is
\emph{tractometry}: assessment of the physical properties of the white
matter along specific tracts \cite{Bells2011-cf}. Though there are
several different available implementations of this overall idea,
the principles are similar \cite{yeatman2012tract, Yendiki2011-ay,
Wassermann2016-iv, ODonnell2009-uu}: tractometry begins by delineating
the parts of the white matter that belong to different major tracts
(i.e. anatomical or functional groups of white matter fibers),
such as the corticospinal tract or arcuate fasciculus, assigning
tractography generated streamlines to ``bundles,'' which approximate
the anatomical tracts, and sampling biophysical properties (such as
fractional anisotropy or mean diffusivity) along the length of these
bundles. Whereas the identification of the anatomical correlates
of tractography-generated streamlines is an open problem, the
correspondence between tractometry's bundles and anatomical tracts is
well supported \cite{Catani2002-vu}. Tract-based diffusion metrics are
therefore appropriate degrees of freedom with which to understand the
white-matter correlates of cognitive function or disease.
